---
title: "Visualize Data"
output:
  html_document:
    df_print: paged
name: ferris tucker
---
## Your Turn 0
install.packages("tidyverse")
install.packages("reshape2")

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, comment="") #"comment" takes away hashtags
library(tidyverse)
```

```{r}
summary(mpg)
```
## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
ggplot(data = mpg) + #addition sign tells ggplot to keep reading, add another layer.
  geom_point(mapping = aes(x=displ, y=hwy))
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
ggplot(mpg, aes(hwy)) +
  geom_histogram(binwidth=1, color=" white", fill="pink")
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
ggplot(mpg, aes(hwy)) +
  geom_histogram(binwidth=3, color="lawngreen", fill="mediumorchid2")
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color=class)) #class is a variable that has color added to each point.
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
q + facet_grid(drv ~ .)
q + facet_grid(drv ~ cyl)
q + facet_wrap(~ class)
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}

```

## Quiz

What will this code do?

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy))
```


***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```